---
title: "run_ravel"
author: "Paul Reiners"
date: "2024-11-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 2. Image preprocessing

### 2.6. Tissue Segmentation


```{r}
library(fslr)
if (have.fsl()) {
  print(fsl_version())
}
```
```{r}
scan_path = '/home/feczk001/shared/projects/S1067_Loes/data/Fairview-ag/anonymized/processed/sub-01_ses-01_space-MNI_brain_mprage.nii.gz'
```

There are different tissue segmentation algorithms available in R. My favorite is the FSL FAST segmentation via the [fslr](https://cran.r-project.org/web/packages/fslr/index.html) package. Let’s produce the tissue segmentation for the scan_reg_n4_brain scan above:

```{r}
img = readNIfTI(scan_path)
print(img)
```

There are different tissue segmentation algorithms available in R. My favorite is the FSL FAST segmentation via the [fslr](https://cran.r-project.org/web/packages/fslr/index.html) package. Let’s produce the tissue segmentation for the scan_reg_n4_brain scan above.

The last line of code produces via the ortho2 function from the fslr package the following visualization of the template.

```{r}
ortho2(scan_reg_n4_brain, crosshairs=FALSE, mfrow=c(1,3), add.orient=FALSE, ylim=c(0,400))
```
We perform a 3-class tissue segmentation on the T1-w image with the FAST segmentation algorithm:

```{r}
scan_reg_n4_brain_seg <- fast(scan_reg_n4_brain, verbose=FALSE, opts="-t 1 -n 3") 
ortho2(scan_reg_n4_brain_seg, crosshairs=FALSE, mfrow=c(1,3), add.orient=FALSE)
```

The object `scan_reg_n4_brain_seg` is an image that contains the segmentation labels `0,1,2` and `3` referring to Background, CSF, GM and WM voxels respectively.

```{r}
writeNIfTI(scan_reg_n4_brain_seg, "segmentation_result.nii.gz")
png("segmentation_visualization.png")
ortho2(scan_reg_n4_brain_seg, crosshairs=FALSE, mfrow=c(1,3), add.orient=FALSE)
dev.off()
```
